\LARGE \bf The Battle for Filter Supremacy: A Comparative Study of the Multi-State Constraint Kalman Filter and Sliding Window Filter

### 2014-12-30 Report/project_report.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

Monkey Style Chinese Kung Fu vs. SWFfer Wet Jet

\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Extended Kalman Filter (EKF)} \label{sec:EKF}
In the Extended Kalman Filter (EKF) solution, vehicle poses and feature positions are simultaneously estimated at each time step by augmenting the filter state with feature positions.
This technique, sometimes referred to as EKF-SLAM, attempts to track pose changes and create a globally consistent map of features by recursively updating the state as new measurements become available.
%Features are commonly parametrized as three-dimensional vectors and are initialized using two-view geometry, but alternative parametrization and initialization schemes exist \cite{Sola:2011:IJCV}.
%In this paper we consider only the three-dimensional parametrization and two-view initialization scheme.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{figs/sensorhead}
    \caption{The sensor head used in our experiments. The IMU measures translational and rotational velocities, while the stereo camera measures the positions of point features. In our experiments, we artificially blinded the stereo camera by using measurements from the left camera only.}
    \label{fig:sensorhead}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Accurate and consistent egomotion estimation is an important part of autonomous vehicles. The combination of visual and inertial sensors provides a relatively inexpensive, compact and complementary hardware suite that can be used on many ground and aerial vehicles. In this work, we compare two modern approaches to egomotion estimation: the Multi-State Costraint Kalman Filter (MSCKF) and the Sliding Window Filter (SWF). Both filters use an Inertial Measurement Unit (IMU) to estimate the motion of a monocular camera and then correct this motion with image observations of salient features. The SWF includes the feature positions in the state estimate itself, while the MSCKF estimates the feature positions in a separate optimization routine. Herein, we compare the performance of the MSCKF and SWF, in error bounds and consistency, on two different datasets with real and synthetic features. We analyze the effect of feature track length and feature density. In general, the SWF is found to be more accurate than the MSCKF. The MSCKF, however, is signficantly faster to compute, has good consistency, and its performance improves with more tracked features. 
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{figs/sensorhead}
    \caption{The sensor head used in our experiments. The IMU measures translational and rotational velocities, while the stereo camera measures the positions of point features. In our experiments, we artificially blinded the stereo camera by using measurements from the left camera only.}
    \label{fig:sensorhead}
\end{figure}

\section{Extended Kalman Filter (EKF)} \label{sec:EKF}
In the Extended Kalman Filter (EKF) solution, vehicle poses and feature positions are simultaneously estimated at each time step by augmenting the filter state with feature positions.
This technique, sometimes referred to as EKF-SLAM, attempts to track pose changes and create a globally consistent map of features by recursively updating the state as new measurements become available.
%Features are commonly parametrized as three-dimensional vectors and are initialized using two-view geometry, but alternative parametrization and initialization schemes exist \cite{Sola:2011:IJCV}.
%In this paper we consider only the three-dimensional parametrization and two-view initialization scheme.

@@
